---
title: "Option Positioning, Pricing, Risk, Model Statistics and Risk Neutral Density"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
---

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(RND)
library(quantmod)
library(lubridate)
library(plotly)
library(rlist)
```

# Basic Data 
```{r, warning=FALSE, message=FALSE}
asset_symbol <- "BABA"
date_today <- today()
spot_price <- getQuote(asset_symbol)$Last
all_chains <- getOptionChain(asset_symbol, Exp = NULL, src = "yahoo")

date_today
spot_price
```


# Extract Rates
```{r, warning=FALSE, message=FALSE, results="hide"}
chain_in_q <- 2
chain <- merge(all_chains[[chain_in_q]][1],
               all_chains[[chain_in_q]][2],
               by.x = "calls.Strike",
               by.y = "puts.Strike")

na.fill(chain, 0)

chain$put_rearranged <- sort(chain$puts.Last, decreasing = FALSE)
chain$call_rearranged <- sort(chain$calls.Last, decreasing = TRUE)

option_exp_list <- names(all_chains)
expiration_date  <- toString(option_exp_list[chain_in_q])
expiration_date <- strptime(expiration_date,
                            format = "%B.%d.%Y", tz = "EST") %>%
                            as.Date(expiration_date, format = "%Y-%m-%d")

days_to_expiration <- as.double(difftime(expiration_date, date_today,
                                         units = "days"))
```

```{r}
rates <- extract.rates(
  calls = chain$call_rearranged,
  puts = chain$put_rearranged,
  s0 = spot_price,
  k = chain$calls.Strike,
  te = days_to_expiration / 365)

rates
```
# Positioning
## Open Interest
```{r}
open_interest <- plot_ly(chain,
                         x = ~calls.Strike, y = ~calls.OI,
                         type = "bar",
                         name = "call OI") %>%
  add_trace(y = ~puts.OI, name = "put OI") %>%
  layout(yaxis = list(title = "Count"), barmode = "group") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = 0,
               yend = max(chain$calls.OI),
               line = list(dash = "dash"))

open_interest
```
## Call-Put Ratio
```{r}
chain$cp_ratio <- chain$calls.OI / chain$puts.OI
cp_ratio <- plot_ly(chain,
                    x = ~calls.Strike, y = ~cp_ratio,
                    type = "bar", name = "Call-Put Ratio") %>%
  layout(yaxis = list(title = "Ratio")) %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = 0,
               yend = max(chain$cp.ratio),
               line = list(dash = "dash"))

cp_ratio
```

## Volume
```{r}
volume <- plot_ly(chain,
                  x = ~calls.Strike, y = ~calls.Vol,
                  type = "bar",
                  name = "call Volume") %>%
  add_trace(y = ~puts.Vol, name = "Put Volume") %>%
  layout(yaxis = list(title = "Count"), barmode = "group") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = 0,
               yend = max(chain$calls.OI),
               line = list(dash = "dash"))

volume
```

# Risk
## Implied Volatility
```{r}
implied_volatility <- plot_ly(chain,
                              x = ~calls.Strike, y = ~calls.IV,
                              name = "Call IV",
                              type = "scatter",
                              mode = "markers") %>%
  add_trace(y = ~puts.IV, name = "Put IV", mode = "markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = 0,
               yend = max(chain$puts.IV),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

implied_volatility
```

# European Options
## Black-Scholes Merton
### ext
```{r}
ext_eu_bsm <- extract.bsm.density(
  r = rates$risk.free.rate,
  y = rates$dividend.yield,
  te = days_to_expiration / 365,
  s0 = spot_price,
  market.calls = chain$calls.Last,
  call.strikes = chain$calls.Strike,
  market.puts = chain$puts.Last,
  put.strikes = chain$calls.Strike,
  lambda = 1, hessian.flag = F)
```

### Pricing
```{r}
eu_bsm_pricing <- price.bsm.option(s0 = spot_price,
                                   k = chain$calls.Strike,
                                   r = rates$risk.free.rate,
                                   te = days_to_expiration,
                                   sigma = ext_eu_bsm$zeta,
                                   y = rates$dividend.yield)

chain$eu_bsm_calls <- eu_bsm_pricing$call
chain$eu_bsm_puts <- eu_bsm_pricing$put

bsm_model_actual <- plot_ly(chain,
                            x = ~calls.Strike, y = ~calls.Last,
                            name = "Market Calls",
                            type = "scatter",
                            mode = "lines+markers") %>%
  add_trace(y = ~eu_bsm_calls, name = "BSM Calls", mode = "lines+markers") %>%
  add_trace(y = ~puts.Last, name = "Market Puts", mode = "lines+markers") %>%
  add_trace(y = ~eu_bsm_puts, name = "BSM Puts", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

bsm_model_actual
```

### Density
```{r}
eu_bsm_density <- get.point.estimate(chain$call_rearranged,
                                     chain$calls.Strike,
                                     rates$risk.free.rate,
                                     days_to_expiration / 365)
chain <- chain[(2:nrow(chain) - 2), ]
chain$eu_bsm_density <- eu_bsm_density

density_eu_bsm <- plot_ly(chain,
                          x = ~calls.Strike, y = ~eu_bsm_density,
                          name = "BSM Risk Neutal Density",
                          type = "scatter", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price, xend = spot_price,
               y = min(chain$eu_bsm_density),
               yend = max(chain$eu_bsm_density)) %>%
  layout(autosize = F, width = 800, height = 500)

density_eu_bsm
```

### Stats
```{r}
eu_bsm_lm_call <- lm(calls.Last~eu_bsm_calls, data = chain)
eu_bsm_lm_put <- lm(calls.Last~eu_bsm_calls, data = chain)

summary(eu_bsm_lm_call)
summary(eu_bsm_lm_put)
```


## Mixture of log-normals
### ext
```{r}
ext_eu_mln <- extract.mln.density(r = rates$risk.free.rate,
                                  y = rates$dividend.yield,
                                  te = days_to_expiration / 365,
                                  s0 = spot_price,
                                  market.calls = chain$calls.Last,
                                  call.strikes = chain$calls.Strike,
                                  market.puts = chain$puts.Last,
                                  put.strikes = chain$calls.Strike,
                                  lambda = 1, hessian.flag = F)
```
### Density
```{r}
density_eu_mln <- dmln(x = chain$calls.Strike,
                       alpha.1 = ext_eu_mln$alpha.1,
                       meanlog.1 = ext_eu_mln$meanlog.1,
                       meanlog.2 = ext_eu_mln$meanlog.2,
                       sdlog.1 = ext_eu_mln$sdlog.1,
                       sdlog.2 = ext_eu_mln$sdlog.2)

chain$eu_mln_density <- density_eu_mln

density_eu_bsm <- plot_ly(chain,
                          x = ~calls.Strike, y = ~eu_mln_density,
                          name = "BSM Risk Neutal Density",
                          type = "scatter", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$eu_mln_density),
               yend = max(chain$eu_mln_density)) %>%
  layout(autosize = F, width = 800, height = 500)

density_eu_bsm
```
### Pricing
```{r}
eu_mln_pricing <- price.mln.option(r = rates$risk.free.rate,
                                   y = rates$dividend.yield,
                                   te = days_to_expiration / 365,
                                   k = chain$calls.Strike,
                                   alpha.1 = ext_eu_mln$alpha.1,
                                   meanlog.1 = ext_eu_mln$meanlog.1,
                                   meanlog.2 = ext_eu_mln$meanlog.2,
                                   sdlog.1 = ext_eu_mln$sdlog.1,
                                   sdlog.2 = ext_eu_mln$sdlog.2)

chain$eu_mln_calls <- eu_mln_pricing$call
chain$eu_mln_puts <- eu_mln_pricing$put

mln_model_actual <- plot_ly(chain,
                            x = ~calls.Strike, y = ~calls.Last,
                            name = "Market Calls",
                            type = "scatter",
                            mode = "lines+markers") %>%
  add_trace(y = ~eu_mln_calls, name = "MLN Calls", mode = "lines+markers") %>%
  add_trace(y = ~puts.Last, name = "Market Puts", mode = "lines+markers") %>%
  add_trace(y = ~eu_mln_puts, name = "MLN Puts", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

mln_model_actual
```
### Stats
```{r}
eu_mln_lm_call <- lm(calls.Last~eu_mln_calls, data = chain)
eu_mln_lm_put <- lm(calls.Last~eu_mln_calls, data = chain)

summary(eu_mln_lm_call)
summary(eu_mln_lm_put)
```

## Generalised Beta
### ext
```{r, message=FALSE, warning=FALSE}
ext_eu_gb <- extract.gb.density(r = rates$risk.free.rate,
                                       y = rates$dividend.yield,
                                       te = days_to_expiration / 365,
                                       s0 = spot_price,
                                       market.calls = chain$calls.Last,
                                       call.strikes = chain$calls.Strike,
                                       market.puts = chain$puts.Last,
                                       put.strikes = chain$calls.Strike,
                                       lambda = 1, hessian.flag = F)
```
### Density
```{r}
chain$eu_gb_density <- dgb(x = chain$calls.Strike,
                           a = ext_eu_gb$a,
                           b = ext_eu_gb$b,
                           v = ext_eu_gb$v,
                           w = ext_eu_gb$w)

density_eu_gb <- plot_ly(chain,
                         x = ~calls.Strike, y = ~eu_gb_density,
                         name = "Genralised Beta Risk Neutal Density",
                         type = "scatter",
                         mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$eu_gb_density),
               yend = max(chain$eu_gb_density)) %>%
  layout(autosize = F, width = 800, height = 500)

density_eu_gb

```
### Pricing
```{r}
eu_gb_pricing <- price.gb.option(r = rates$risk.free.rate,
                                 y = rates$dividend.yield,
                                 te = days_to_expiration / 365,
                                 s0 = spot_price,
                                 k = chain$calls.Strike,
                                 a = ext_eu_gb$a,
                                 b = ext_eu_gb$b,
                                 v = ext_eu_gb$v,
                                 w = ext_eu_gb$w)

chain$eu_gb_calls <- eu_gb_pricing$call
chain$eu_gb_puts <- eu_gb_pricing$put

gb_model_actual <- plot_ly(chain,
                           x = ~calls.Strike, y = ~calls.Last,
                           name = "Market Calls",
                           type = "scatter",
                           mode = "lines+markers") %>%
  add_trace(y = ~eu_gb_calls, name = "GB Calls", mode = "lines+markers") %>%
  add_trace(y = ~puts.Last, name = "Market Puts", mode = "lines+markers") %>%
  add_trace(y = ~eu_gb_puts, name = "GB Puts", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

gb_model_actual
```
### Stats
```{r}
eu_gb_lm_call <- lm(calls.Last~eu_gb_calls, data = chain)
eu_gb_lm_put <- lm(calls.Last~eu_gb_calls, data = chain)

summary(eu_gb_lm_call)
summary(eu_gb_lm_put)
```

## Edgeworth Expansion
### ext
```{r}
ext_eu_ew <- extract.ew.density(r = rates$risk.free.rate,
                                       y = rates$dividend.yield,
                                       te = days_to_expiration / 365,
                                       s0 = spot_price,
                                       market.calls = chain$calls.Last,
                                       call.strikes = chain$calls.Strike,
                                       lambda = 1, hessian.flag = F)
```
### Density
```{r}
chain$eu_ew_density <- dew(x = chain$calls.Last,
                           r = rates$risk.free.rate,
                           y = rates$dividend.yield,
                           te = days_to_expiration / 365,
                           s0 = spot_price,
                           sigma = ext_eu_ew$sigma,
                           skew = ext_eu_ew$skew,
                           kurt = ext_eu_ew$kurt)

density_eu_ew <- plot_ly(chain,
                         x = ~calls.Strike, y = ~eu_ew_density,
                         name = "Edgeworth Expansion Risk Neutal Density",
                         type = "scatter",
                         mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$eu_ew_density),
               yend = max(chain$eu_ew_density)) %>%
  layout(autosize = F, width = 800, height = 500)

density_eu_ew
```
### Pricing
```{r}
eu_ew_pricing <- price.ew.option(k = chain$calls.Last,
                                 r = rates$risk.free.rate,
                                 y = rates$dividend.yield,
                                 te = days_to_expiration / 365,
                                 s0 = spot_price,
                                 sigma = ext_eu_ew$sigma,
                                 skew = ext_eu_ew$skew,
                                 kurt = ext_eu_ew$kurt)

chain$eu_ew_calls <- eu_ew_pricing$call
chain$eu_ew_puts <- eu_ew_pricing$put

ew_model_actual <- plot_ly(chain,
                          x = ~calls.Strike, y = ~calls.Last,
                          name = "Market Calls",
                          type = "scatter",
                          mode = "lines+markers") %>%
  add_trace(y = ~eu_ew_calls, name = "EW Calls", mode = "lines+markers") %>%
  add_trace(y = ~puts.Last, name = "Market Puts", mode = "lines+markers") %>%
  add_trace(y = ~eu_ew_puts, name = "EW Puts", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

ew_model_actual
```
### Stats
```{r}
eu_ew_lm_call <- lm(calls.Last~eu_ew_calls, data = chain)
eu_ew_lm_put <- lm(calls.Last~eu_ew_calls, data = chain)

summary(eu_ew_lm_call)
summary(eu_ew_lm_put)
```

## Shimko 
### ext
```{r}
ext_eu_shimko <- extract.shimko.density(
  market.calls = chain$calls.Last,
  call.strikes = chain$calls.Strike,
  r = rates$risk.free.rate,
  y = rates$dividend.yield,
  te = days_to_expiration / 365,
  s0 = spot_price,
  lower = -10, upper = +10)
```
### Density
```{r}
chain$eu_shimko_density <- dshimko(r = rates$risk.free.rate,
                                   te = days_to_expiration / 365,
                                   k = chain$calls.Last,
                                   s0 = spot_price,
                                   y = rates$dividend.yield,
                                   a0 = ext_eu_shimko$implied.curve.obj$a0,
                                   a1 = ext_eu_shimko$implied.curve.obj$a1,
                                   a2 = ext_eu_shimko$implied.curve.obj$a2)

density_eu_shimko <- plot_ly(chain, x = ~calls.Strike, y = ~eu_shimko_density,
                      name = "Shimko Risk Neutal Density",
                      type = "scatter", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$eu_shimko_density),
               yend = max(chain$eu_shimko_density)) %>%
  layout(autosize = F, width = 800, height = 500)

density_eu_shimko
```
### Pricing
```{r}
eu_shimko_call <- numeric(length(chain$calls.Strike))
for (i in seq_len(length(chain$calls.Strike))) {
    eu_shimko_call[i] <- price.shimko.option(
      k = chain$calls.Strike[i],
      r = rates$risk.free.rate,
      y = rates$dividend.yield,
      te = days_to_expiration / 365,
      s0 = spot_price,
      a0 = ext_eu_shimko$implied.curve.obj$a0,
      a1 = ext_eu_shimko$implied.curve.obj$a1,
      a2 = ext_eu_shimko$implied.curve.obj$a2)$put
                                         }

eu_shimko_put <- numeric(length(chain$calls.Strike))
for (j in seq_len(length(chain$calls.Strike))) {
    eu_shimko_put[j] <- price.shimko.option(
      k = chain$calls.Strike[j],
      r = rates$risk.free.rate,
      y = rates$dividend.yield,
      te = days_to_expiration / 365,
      s0 = spot_price,
      a0 = ext_eu_shimko$implied.curve.obj$a0,
      a1 = ext_eu_shimko$implied.curve.obj$a1,
      a2 = ext_eu_shimko$implied.curve.obj$a2)$call
                                         }

chain$eu_shimko_calls <- eu_shimko_call
chain$eu_shimko_puts <- eu_shimko_put

shimko_model_actual <- plot_ly(chain,
                               x = ~calls.Strike, y = ~calls.Last,
                               name = "Market Calls",
                               type = "scatter",
                               mode = "lines+markers") %>%
  add_trace(y = ~eu_shimko_calls, name = "EW Calls", mode = "lines+markers") %>%
  add_trace(y = ~puts.Last, name = "Market Puts", mode = "lines+markers") %>%
  add_trace(y = ~eu_shimko_puts, name = "EW Puts", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

shimko_model_actual
```
### Stats
```{r}
eu_shimko_lm_call <- lm(calls.Last~eu_shimko_calls, data = chain)
eu_shimko_lm_put <- lm(calls.Last~eu_shimko_puts, data = chain)

summary(eu_shimko_lm_call)
summary(eu_shimko_lm_put)
```


# American Options 
## Mixture of log-normals 
### ext   
```{r, results="hide"}
ext_am_mln <- extract.am.density(r = rates$risk.free.rate,
                                        te = days_to_expiration / 365,
                                        s0 = spot_price,
                                        market.calls = chain$calls.Last,
                                        market.puts = chain$puts.Last,
                                        strikes = chain$calls.Strike,
                                        lambda = 1, hessian.flag = F)
ext_am_mln$p.3 <- 1 - ext_am_mln$p.1 - ext_am_mln$p.2
```

### Density    
```{r}
chain$am_mln_density <- dmln.am(x = chain$calls.Strike,
                                       u.1 = ext_am_mln$u.1,
                                       u.2 = ext_am_mln$u.2,
                                       u.3 = ext_am_mln$u.3,
                                       sigma.1 = ext_am_mln$sigma.1,
                                       sigma.2 = ext_am_mln$sigma.2,
                                       sigma.3 = ext_am_mln$sigma.3,
                                       p.1 = ext_am_mln$p.1,
                                       p.2 = ext_am_mln$p.2)


am_expected_f0 <- sum(c(ext_am_mln$p.1,
                        ext_am_mln$p.2,
                        ext_am_mln$p.3) *
                  exp(c(ext_am_mln$u.1,
                        ext_am_mln$u.2,
                        ext_am_mln$u.3) +
                     (c(ext_am_mln$sigma.1,
                        ext_am_mln$sigma.2,
                        ext_am_mln$sigma.3)^ 2) / 2))

density_am <- plot_ly(chain, x = ~calls.Strike, y = ~am_mln_density,
                      name = "American Mixture of Log Normals Risk Neutal Density",
                      type = "scatter", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$am_mln_density),
               yend = max(chain$am_mln_density),
               line = list(dash = "dash")) %>%
  add_segments(name = "Expected mean value at expiration",
               x = am_expected_f0,
               xend = am_expected_f0,
               y = min(chain$am_mln_density),
               yend = max(chain$am_mln_density),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)

density_am
```

### Pricing  
```{r, warning=FALSE}
chain$am_mln_calls <- numeric(length(chain$calls.Strike))
chain$am_mln_puts  <- numeric(length(chain$calls.Strike))

for (i in seq_len(length(chain$calls.Strike))) {
  if (chain$calls.Strike[i] < am_expected_f0) {
    chain$am_mln_calls[i] <- price.am.option(
      k = chain$calls.Strike[i],
      r = rates$risk.free.rate,
      te = days_to_expiration / 365,
      w = ext_am_mln$w.1,
      u.1 = ext_am_mln$u.1,
      u.2 = ext_am_mln$u.2,
      u.3 = ext_am_mln$u.3,
      sigma.1 = ext_am_mln$sigma.1,
      sigma.2 = ext_am_mln$sigma.2,
      sigma.3 = ext_am_mln$sigma.3,
      p.1 = ext_am_mln$p.1,
      p.2 = ext_am_mln$p.2)$call.value

    chain$am_mln_puts[i] <- price.am.option(
      k = chain$calls.Strike[i],
      r = rates$risk.free.rate,
      te = days_to_expiration / 365,
      w = ext_am_mln$w.2,
      u.1 = ext_am_mln$u.1,
      u.2 = ext_am_mln$u.2,
      u.3 = ext_am_mln$u.3,
      sigma.1 = ext_am_mln$sigma.1,
      sigma.2 = ext_am_mln$sigma.2,
      sigma.3 = ext_am_mln$sigma.3,
      p.1 = ext_am_mln$p.1,
      p.2 = ext_am_mln$p.2)$put.value

  }  else {

    chain$am_mln_calls[i] <- price.am.option(
      k = chain$calls.Strike[i],
      r = rates$risk.free.rate,
      te = days_to_expiration / 365,
      w = ext_am_mln$w.2,
      u.1 = ext_am_mln$u.1,
      u.2 = ext_am_mln$u.2,
      u.3 = ext_am_mln$u.3,
      sigma.1 = ext_am_mln$sigma.1,
      sigma.2 = ext_am_mln$sigma.2,
      sigma.3 = ext_am_mln$sigma.3,
      p.1 = ext_am_mln$p.1,
      p.2 = ext_am_mln$p.2)$call.value

    chain$am_mln_puts[i] <- price.am.option(
      k = chain$calls.Strike[i],
      r = rates$risk.free.rate,
      te = days_to_expiration / 365,
      w = ext_am_mln$w.1,
      u.1 = ext_am_mln$u.1,
      u.2 = ext_am_mln$u.2,
      u.3 = ext_am_mln$u.3,
      sigma.1 = ext_am_mln$sigma.1,
      sigma.2 = ext_am_mln$sigma.2,
      sigma.3 = ext_am_mln$sigma.3,
      p.1 = ext_am_mln$p.1,
      p.2 = ext_am_mln$p.2)$put.value
     }
}

```

```{r}
am_model_actual <- plot_ly(chain, x = ~calls.Strike, y = ~calls.Last,
                          name = "Market Calls",
                          type = "scatter",
                          mode = "lines+markers") %>%
  add_trace(y = ~am_mln_calls, name = "MixLN Calls", mode = "lines+markers") %>%
  add_trace(y = ~puts.Last, name = "Market Puts", mode = "lines+markers") %>%
  add_trace(y = ~am_mln_puts, name = "MixLN Puts", mode = "lines+markers") %>%
  add_segments(name = "Spot Price",
               x = spot_price,
               xend = spot_price,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  add_segments(name = "Expected mean value at expiration",
               x = am_expected_f0,
               xend = am_expected_f0,
               y = min(chain$calls.Last),
               yend = max(chain$calls.Last),
               line = list(dash = "dash")) %>%
  layout(autosize = F, width = 800, height = 500)
am_model_actual
```

### Stats
```{r, echo=FALSE}
am_mln_lm_call <- lm(calls.Last~am_mln_calls, data = chain)
am_mln_lm_put <- lm(puts.Last~am_mln_puts, data = chain)

am_expected_f0
summary(am_mln_lm_call)
summary(am_mln_lm_put)
```








